---
title: "mlr3 notes"
author: "Linlin Yin"
date: "April 16, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Visulization To-Do List
* Model Specific (Use functions in other package)
    * decision tree
    * Any other models?
* Learner (data)
    * Histgram; Boxplot
* resampling related: Robust?
    * Performance distribution in resampling (AUC, accuracy, ...)
    * Feature importantce in resampling
* Feature selection related: Simialr to resampling?
    * how many times selected in resampling
    * feature importance
* Benchmark: Comparing different models
    * Performance distribution of different models
    * Prediction results of different models (sample level, something like predicted correctly by all models, heatmap?)
    * ROC and PR curve


# Tests


```{r}
library(mlr3)
```


```{r}
task = Task$new("iris", task_type = "classif", backend = iris)
task


task$formula
task$cbind(data.frame(foo = 1:150))
task$formula
```


# Tasks

Let’s assume we want to create a simple regression task using the mtcars data set from the package datasets to predict the column "mpg" (miles per gallon). We only take the first two features here to keep the output in the following examples short.


```{r}
data("mtcars", package = "datasets")
data = mtcars[, 1:3]

task_mtcars = TaskRegr$new(id = "cars", backend = data, target = "mpg")
print(task_mtcars)

```


## Predefined tasks

```{r}

as.data.table(mlr_tasks)

task_iris = mlr_tasks$get("iris")
print(task_iris)



task_iris$nrow
task_iris$ncol

task_iris$head(n = 3)

# retrieve data for rows with ids 1, 51, and 101
task_iris$data(rows = c(1, 51, 101))


head(task_mtcars$row_ids)

task_iris$data()
as.data.table(task_iris)


task_iris$feature_names
task_iris$target_names

```


## Roles
It is possible to assign special roles to (subsets of) rows and columns.
For example, the previously constructed mtcars task has the following column roles:

```{r}
task_mtcars$col_roles


library("data.table")


data = as.data.table(mtcars[, 1:3], keep.rownames = TRUE)
task = TaskRegr$new(id = "cars", backend = data, target = "mpg")

task$feature_names

#we need to change the role of the row names column rn and remove it from the set of active features. As this is a unique string column, most machine learning algorithms will have problems to process this feature.
#We need to change it to a label instead of feature
task$set_col_role("rn", new_roles = "label")
# also vanished from "data" and "head"
task$data(rows = 1:2)
task$head(2)
```
Rows can have two different roles:
1. Role "use": Rows that are generally available for model fitting (although they may also be used as test set in resampling). This is the default role.
2. Role "validation": Rows that are held back (see below). Rows which have missing values in the target column upon task creation are automatically moved to the validation set.

## Task Mutators
All these operations only change the view on the data, without creating a copy of it, but modify the task in-place.

The original data set stored in the original mlr3::DataBackend is not altered in any way.

```{r}
task = mlr_tasks$get("iris")
task$select(c("Sepal.Width", "Sepal.Length")) # keep only these features
task$filter(1:3) # keep only these rows
task$head()

task$cbind(data.table(foo = letters[1:3])) # add column foo
task$head()

```


# Introduction to Resampling
```{r}
library(mlr3)
task = mlr_tasks$get("iris")
learner = mlr_learners$get("classif.rpart")

mlr_resamplings$keys()



```


# Benchmark 

```{r}
tasks = mlr_tasks$mget(c("iris", "sonar"))
learners = mlr_learners$mget(c("classif.featureless", "classif.rpart"))
resamplings = mlr_resamplings$mget("holdout")

design = expand_grid(tasks, learners, resamplings)
print(design)

set.seed(123)
bmr = benchmark(design)
bmr

# performance for all conducted experiments
as.data.table(bmr)

# aggregated performance values
bmr$aggregated(objects = FALSE)

# Overview of of resamplings that were conducted internally
rrs = bmr$resample_results
print(rrs)

# Extract first ResampleResult
rr = bmr$resample_result(hash = rrs$hash[1])
print(rr)

# Extract predictions of first experiment of this resampling
head(as.data.table(rr$experiment(1)$prediction))


```



