---
title: "mlr3 vis development"
author: "Linlin Yin"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Test for visulization functions from mlr to mlr3

```{r}
library(mlr3)
library(ggplot2)
library(data.table)
library(dplyr)

#devtools::load_all("d:/source/machineLearning_mlr/mlr3vis/")
library(mlr3vis)
library(checkmate)
```

mlr: https://mlr.mlr-org.com/articles/tutorial/predict.html  

mlr3: https://mlr3book.mlr-org.com/  

## plotLearnerPrediction

Questions: 
1. Not sure about the Cross validation part. In mlr1, pred.cv = cvResult$predict; But how can we get predict result in mlr3 for ResampleResult object?
2. To plot the "grid", How to make new task in mlr3? taskGrid=TaskRegr$new(backend = grid) doesn't work: argument "target" is missing.

```{r}

task = mlr_tasks$get("iris")
learner = mlr_learners$get("classif.rpart")

plotLearnerPrediction(learner=learner,task=task)

```

## benchmark related
```{r}

# get some example tasks
tasks = mlr_tasks$mget(c("pima", "sonar", "spam"))

# set measures for all tasks: accuracy (acc) and area under the curve (auc)
measures = mlr_measures$mget(c("classif.acc", "classif.auc"))
tasks = lapply(tasks, function(task) { task$measures = measures; task })

# get a featureless learner and a classification tree
learners = mlr_learners$mget(c("classif.featureless", "classif.rpart"))

# let the learners predict probabilities instead of class labels (required for AUC measure)
learners$classif.featureless$predict_type = "prob"
learners$classif.rpart$predict_type = "prob"

# compare via 10-fold cross validation
resamplings = mlr_resamplings$mget("cv")

# create a BenchmarkResult object
design = expand_grid(tasks, learners, resamplings)
print(design)


bmr = benchmark(design)

#bmr
#bmr$aggregated(objects = FALSE)
#bmr$aggregated(objects = FALSE)[, list(acc = mean(classif.acc), auc = mean(classif.auc)), by = "learner_id"]





```


```{r}

plotBMRBoxplots(bmr)

```


```{r}


plotBMRRanksAsBarChart(bmr)
```





